\subsection{Introduction}
\begin{itemize}
    \item Can figure out Big-O runtime of algorithms
\end{itemize}

\subsection{Basic Data Structures}
\begin{itemize}
    \item Array: O(1) access, O(N) modifications to length
    \item Linked List: O(N) access, O(1) modifications at start/end, O(N) elsewhere.
\end{itemize}

\subsection{Nested Loops}
\begin{itemize}
    \item Each loop takes O(N) time.
    \item Adding a nested loop adds a power to the N.
    \item Eg. a for loop in a for loop is $O(N^2)$.
\end{itemize}

\subsection{A Connected Component Algorithm}
\begin{itemize}
    \item Gets nodes in the same connected component.
    \item Traverses nodes and edges, so it's O(N+M).
\end{itemize}

\subsection{Binary Search}
\begin{itemize}
    \item Splits a sorted range into two, and gets middle.
    \item Operates based on the middle value.
    \item Time Complexity: O(logN)
\end{itemize}

\subsection{Merging Two Lists}
\begin{itemize}
    \item Creates a new list, but has to traverse both lists.
    \item Time Complexity: O(N).
\end{itemize}

\subsection{Mergesort}
\begin{itemize}
    \item Splits up a list into 2, then sorts both and merges.
    \item Time Complexity: O(NlogN).
\end{itemize}

\subsection{Tower of Hanoi}
\begin{itemize}
    \item Needs to move discs from 1 tower to another.
    \item Time Complexity: $O(2^N)$.
\end{itemize}

\subsection{Multiplying Big Integers}
\begin{itemize}
    \item Karatsuba's Algorithm for enhanced multiplication.
    \item Time Complexity: $O(N^{\log_2{3}})$
\end{itemize}